HERMES : Hybrid ERror-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2021-12-02 hermes_paper/hermes_paper.tex
Fixed bug in biblio
several updates

Recurrent neural networks are appealing to tackle our forecasting problem due to their capability of leveraging external data.  Recently, hybrid models combining DNN architectures with widespread statistical models to deal with seasonality and trends have been proposed, see for instance  \citep{zhang2003time,jianwei2019novel,bandara2020lstm}. The approach providing the most striking results was proposed in  \citep{smyl2020hybrid} in the context of the M4 forecasting competition \citep{makridakis2020m4}.  Given a large dataset, a per-time-series multiplicative exponential smoothing model is introduced to estimate simple but fundamental components for each time series and compute a first prediction. Then a global recurrent neural network is trained on the entire dataset to correct errors of the previous exponential smoothing models. %With this process, the hybrid approach succeeds at mixing strengths of both model families: robustness of the time series specific parametric models and the power of neural network at learn complex dynamics on large dataset. 
%However, the hybrid model has not been designed to deal with external signals even if it include a neural network.

@@

The paper is organized as follow. Section~\ref{sec:hybrid} describes our hybrid framework. Then, we present our new fashion dataset in Section~\ref{sec:dataset}. Section~\ref{sec:exp} describes our results and comparisons with several benchmarks. Finally, we conclude our paper and detail research perspectives in Section~\ref{sec:discussion} and Section~\ref{sec:conclusion}.

\section{Hybrid model with external signals}
\label{sec:hybrid}
%We introduce a new hybrid approach for time series forecasting  composed of two parts: a first per time series parametric model with seasonal component and a global RNN. We use a per time series statistical model to learn local behaviour and to normalize sequences before feeding them to the neural network.
%We introduce a new hybrid approach for time series forecasting  composed of two parts: a first per time series parametric model with seasonal component and a global neural network framework composed of two RNN. We use a per time series statistical model to learn local behaviour, to normalize sequences by removing trends and seasonality,  and to compute a first forecast. Then, we use two recurrent neural networks and weak signals to correct, if needed, the predictions provided by the first collection of parametric models.
We introduce a new hybrid approach for time series forecasting  composed of two parts: first per-time-series parametric models, the predictors, and a global error-corrector neural network train on all the time series, the corrector. We use  per-time-series parametric models to learn local behaviour, to normalize sequences by removing trends and seasonality,  and to compute a first forecast. Then, gathering information of the first predictions and external variables, we use a recurrent neural networks to correct the predictions provided by the first collection of per-time-series models.

@@

At this stage, we want to train a global RNN, trained on all the N sequences and able to understand and correct the weaknesses of the first per-time-series parametric models. This task requires a thorough data pre-processing for two main reasons. Firstly, we want to give to the RNN the best input in order to understand the first collection of forecasts and predict their future errors. Secondly,as we did not suppose any assumption about the scale of our time series, we have to carefully normalize them before feeding our RNN with.
In this way, we define the following pre-processing :
%At this stage, we can write that for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
%$$
%\ts^n_{T+i} = \tspred^{stat,n}_{T+i|T} + \varepsilon^n_{T+i}\,,
%$$
%In this paper, we introduce a model based on a latent regime. In regime 0, the first parametric forecast succeeds at catching all the information of the $n$-th sequence and the final forecast of our framework is the prediction of the per-time-series parametric model. Conversely, in regime 1, the first parametric forecast is unaccurate and it remains a residual random error term that can be estimated. % quantity that we note $\remainder$. 
%Conditionally on $\{\fullts^n\}_{1\leqslant n\leqslant N}$, our regime-switching model is:

@@

We provide the first dataset dedicated to fashion trends forecasting. Our fashion dataset is built with a high throughput computer vision system analysing every day images shared on social networks. Aggregating detected clothes by trends, we create for the first time thousands of time series representing fashion trends life on social media. Our sequences have all 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values. Each time series is normalized in order to remove social networks biases and their values lie between 0 and 1. The proposed fashion dataset contains $\numberts$ anonymized fashion trends for men and women, on 9 different categories and 5 geozones. An overview of it can be found in table 1.

@@

To train our hybrid model, we split our dataset into three blocks, train, eval and test sets. We use the 3 first years as our train set, we keep the 4th year for our eval set and we hide the last year for our test set. We train our hyrid model to compute a one-year ahead prediction, $\lag$ equal to 52, and we set the window size $\window$ equal to 104.
Using the two first year of our train set, we fit a first per-time-series parametric model for each time series. With the resulting collection of local models, we compute a first forecast of the third year for each sequence. Using these forecasts, we preprocess our time series and finally determine our RNN inputs. We can, then, train our RNN at understanding and correcting the previous collection of parametric model's forecasts. In the same way, for the eval set, we fit a second time our per-time-series predictors using the three first years and we forecast the fourth year. We preprocess our time series and we evaluate how our error-corrector RNN is able to improve the first collection of predictions of the fourth year.
At the end, we repeat the same process for the last year and compute our final accuracy measures. An example of our splitting is shown in  Figure~\ref{fig:train_eval_test_set}.
%We train our hyrid model to compute a one-year ahead prediction with $\window$ equal to 104 and a $\lag$ equal to 52. For each time series, we fitted 3 per-time-series parametric models: We fit the first one using the 2 first years and compute a forecast of the thrid year.

@@

For the first parametric per-time-series models, we used existing Python or R librarys to estimate the different parameters $\statparam^n$. These parameters could move during the training of the hybrid model proposed during the M4 competition. In our framework, there are fixed during the training of the recurrent models. In this section we propose two versions of HERMES depending of the choice of local parametric models. The first one use as predictors an additive exponential smoothing model as a reference close to \cite{smyl2020hybrid}. The second one use as predictors the TBATS model of \cite{doi:10.1198/jasa.2011.tm09771} and  achieves striking accuracy results on our fashion dataset. For the neural network part, we built an architecture summarized in Figure~\ref{fig:rnn_architecture}. It is composed of 3 LSTM layer of shape 50 and a final Dense layer to provide the correct output dimension. We use a classical Adam optimizer with a learning rate equal to 0.005 and a batch size equal to 64. For our loss function, we tested several metrics and we finally converged on the following one :

@@

Against these models, we propose two versions of our hybrid model (hermes) called respectively hermes-ets and herles-tbats according to the per-time-series model choice.
%Against these models, we propose two versions of our regime switching hybrid recurrent model \textit{rshm}. The first one, that we name \textit{rshm-ets}, is the hybrid model with an additive exponential smoothing model as parametric model. For the second one, we use the TBATS approach as paramteric model and we named it \textit{rshm-tbats}. 
%To reach a higher accuracy level we also propose an ensembling (\textit{ensembling} of our hybrid approach using the FFORMA method created during the M4 competition, see \citep{fforma}). 
For our two versions, we propose a version without our weak signal called \textit{hermes-ets} and \textit{hermes-tbats}. Then we evaluate our hybrid framework with the inclusion of our weak signals (ws) referred to as \textit{hermes-ets-ws} and \textit{hermes-tbats-ws}. In order to provide a fair comparison, we also train a \textit{lstm} with the weak signals named \textit{lstm-ws}.

@@

Detecting emerging and declining trends is a crucial issue for the fashion industry. A correct or incorrect prediction could lead to good returns or massive waste due to overstock or unsold clothes. In a given year, we define an increasing trend as a trend that does more than 10\% of growth in terms of Year and Year.In the same way, we define a decreasing trend as a trend that declines by 10\% or more. We classify other trends as flat trends. On the test set, the year 2019, we have 1871 increasing trends, 2016 decreasing trends and 6113 flat trends. In addition to the accuracy metrics, we also compare the different methods on this classification task and especially difference between methode using weak signal or not.

@@

For our 3 metrics and for each model, we compute the average on all our sequences \numberts on the final year. Results are displayed in the Table~\ref{tab:metricresults}. For our model using neural networks, we trained 10 models with different seeds and compute the average and the standard deviation for the three metrics. For the statistical models, we can see a large domination of the TBATS model with an OWA equal to 0.850. It is one of the main reasons why we use this model on one of our HERMES frameworks as the predictor model. However, we can see that the full LSTM model \textit{lstm} is the best model over our benchmark candidates with a OWA equal to 0.825.

Considering our new HERMES approach, we see a large domination of our \textit{hermes-tbats} version with a OWA equal to 0.816 and a strong stability across the different trainings. Regarding \textit{hermes-ets}, we see a huge increase compared to its predictor choice \textit{ets} with a descrease from 0.937 to 0.875 in term of OWA. However, its accuracy remains low in comparison to the \textit{lstm} benchmarck or our HERMES's second version using Tbats. In Figure~\ref{fig:hybrid-examples}, we displayed some examples of our HERMES model and some weaknessess that it is able to understand and accurately correct.

@@

An interesting constat is that models using our weak signals underperform their relative without-weak-signals models on all our 3 metrics. We see an exception for our \textit{hermes-tabts-ws} that slightly outperform it relative \textit{hermes-tabts} in term of MASE (0.713 compare to 0.715) but its not clearly significative compare to the standard deviation. The impact of our weak signal is reveal with our classification result.

When we compare our classification results between the \textit{tbats} model and our hybrid method \textit{hermes-tbats} given in Table~\ref{tab:tbatsclass}, we note an impresive diminution of that we called an "unforgiveable error" : forecast an increase instead of a decrease and vice versa. We divide the number of this error by 3 with only a slightly decrease of the number of correct increase/decrease prediction. However, with our weak signals, we see that \textit{hermes-tbats-ws} is able to catch twice as much as its relative model without weak signal while keeping a relatively low number of "unforgivable error".

@@

In addition to our results on our fashion dataset gathering 10000 time series, we also investigate the behaviours of our HERMES model when it is trained on smaller dataset. We did 2 experiences, we train our models on a dataset of 1000 time series and on a dataset of 100 time series. Results are given in Table~\ref{tab:1000metricresults} and Table~\ref{tab:100metricresults}.

With these investigations, we can make two remarks. First, our hybrid framework \textit{hermes-tbats} achieves the first position in term of global accuracy on both datasets. Due to the strengh of its per-time-series predictor TBATS, our hybrid model succeds at correcting some of its weaknesses and logically reach a striking final accuracy. Secondly, we can note that the accuracy of the full neural network \textit{lstm} decrease according to the dataset size. With a small dataset of 100 time series, a local statistical model like \textit{tbats} or \textit{stlm} can largely outperform its accuracy level. In fact, neural networks need a large amount of data to perform well on a complex task. However, with our hybrid framework, the neural network task is largely easier than create a full prediction from scratch. Consequently our approach needs less data to succeed at performing well.

@@

With our results, we can make several interesting conclusions. Firstly, our new HERMES hybrid framework is a really promising framework. By mixing the performance of local parametric models and a global DNN, our \textit{hermes-tbats} version clearly outperform traditional statistical methods and full neural network models. Furthermore, this framework is totally suited for dealing with external signals. With a fine pre-processing and a well-designed architecture, our hybrid framework succeed at leveraging our complex extra data and reach impressive accuracy level in term of classification. Secondly, our results bring to light the quality of our new Fashion dataset. We saw that the full LSTM model \textit{lstm} outperforms all time series specific models when it is trained with the biggest dataset of 10000 time series but not with the smaller ones. This shows that complex neural network architectures involve large amount of data to be train and our full dataset is well suited for this. Finally, with the addition of our weak signals, we give a totally new dimension to our new hybrid architecture and our fashion dataset. Our results show that our external weak signals hide a complex but usable predictive power by our HERMES model. However, we believe that it remains a lot of ways to explore in order to leverage the full potential of these chaotic signals.

@@

\bibliography{hermes_paper}
\bibliographystyle{hermes_paper}

@@

\%section{Fashion Dataset overview}

>>>>

Recurrent neural networks are appealing to tackle our forecasting problem due to their capability of leveraging external data.  Recently, hybrid models combining deep neural network (DNN) architectures with widespread statistical models to deal with seasonality and trends have been proposed, see for instance  \citep{zhang2003time,jianwei2019novel,bandara2020lstm}. The approach providing the most striking results was proposed in  \citep{smyl2020hybrid} in the context of the M4 forecasting competition \citep{makridakis2020m4}.  Given a large dataset, a per-time-series multiplicative exponential smoothing model is introduced to estimate simple but fundamental components for each time series and compute a first prediction. Then a global recurrent neural network is trained on the entire dataset to correct errors of the previous exponential smoothing models. %With this process, the hybrid approach succeeds at mixing strengths of both model families: robustness of the time series specific parametric models and the power of neural network at learn complex dynamics on large dataset. 
%However, the hybrid model has not been designed to deal with external signals even if it include a neural network.

@@

The paper is organized as follow. Section~\ref{sec:hybrid} describes our hybrid framework. Then, we present our new fashion dataset in Section~\ref{sec:dataset}. Section~\ref{sec:exp} describes our results and comparisons with several benchmarks. Finally, we detail research perspectives and conclude our paper in Section~\ref{sec:discussion} and Section~\ref{sec:conclusion}.

\section{Hybrid model with external signals}
\label{sec:hybrid}
%We introduce a new hybrid approach for time series forecasting  composed of two parts: a first per time series parametric model with seasonal component and a global RNN. We use a per time series statistical model to learn local behaviour and to normalize sequences before feeding them to the neural network.
%We introduce a new hybrid approach for time series forecasting  composed of two parts: a first per time series parametric model with seasonal component and a global neural network framework composed of two RNN. We use a per time series statistical model to learn local behaviour, to normalize sequences by removing trends and seasonality,  and to compute a first forecast. Then, we use two recurrent neural networks and weak signals to correct, if needed, the predictions provided by the first collection of parametric models.
We introduce a new hybrid approach for time series forecasting  composed of two parts: a collection of per-time-series parametric models, the predictors, and a global error-corrector neural network train on all the time series, the corrector. We use  per-time-series parametric models to learn local behaviour, to normalize sequences by removing trends and seasonality,  and to compute a first forecast. Then, gathering information of the first predictions and external variables, we use a recurrent neural networks to correct the predictions provided by the first collection of per-time-series models.

@@

At this stage, we want to train a global RNN, trained on all the N sequences and able to understand and correct the weaknesses of the first per-time-series parametric models. This task requires a thorough data pre-processing for two main reasons. Firstly, we want to give to the RNN the best input in order to understand the initial collection of forecasts and predict their future errors. Secondly, as we did not suppose any assumption about the scale of our time series, we have to carefully normalize them before feeding our RNN with.
In this way, we define the following pre-processing :
%At this stage, we can write that for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
%$$
%\ts^n_{T+i} = \tspred^{stat,n}_{T+i|T} + \varepsilon^n_{T+i}\,,
%$$
%In this paper, we introduce a model based on a latent regime. In regime 0, the first parametric forecast succeeds at catching all the information of the $n$-th sequence and the final forecast of our framework is the prediction of the per-time-series parametric model. Conversely, in regime 1, the first parametric forecast is unaccurate and it remains a residual random error term that can be estimated. % quantity that we note $\remainder$. 
%Conditionally on $\{\fullts^n\}_{1\leqslant n\leqslant N}$, our regime-switching model is:

@@

We provide the first dataset dedicated to fashion trends forecasting. Our fashion dataset is built with a high throughput computer vision system analysing every day images shared on social networks. Aggregating detected clothes by trends, we create for the first time thousands of time series representing fashion trends life on social media. Our sequences have all 261 time steps, from 2015-01-05 to 2019-12-31 with weekly values and no missing values. Each time series is normalized in order to remove social networks biases and their values lie between 0 and 1. The proposed fashion dataset contains $\numberts$ anonymized fashion trends for men and women, on 9 different categories and 5 geozones. An overview of it can be found in Table 1.

@@

To train our hybrid model, we split our dataset into three blocks, train, eval and test sets. We use the 3 first years as our train set, we keep the 4th year for our eval set and we hide the last year for our test set. We train our hyrid model to compute a one-year ahead prediction, $\lag$ equal to 52, and we set the window size $\window$ equal to 104.
Using the two first year of our train set, we fit a first per-time-series parametric model for each time series. With the resulting collection of local models, we compute a first forecast of the third year for each sequence. Using these forecasts, we preprocess our time series and finally determine our RNN inputs. We can, then, train our RNN at understanding and correcting the previous collection of parametric model's forecasts. In the same way, for the eval set, we fit a second time our per-time-series predictors using the three first years and we forecast the fourth year. We preprocess our time series and we evaluate how our error-corrector RNN is able to improve the first collection of predictions of the fourth year.
At the end, we repeat the same process for the fifth year and compute our final accuracy measures. An example of our temporal split is shown in  Figure~\ref{fig:train_eval_test_set}.
%We train our hyrid model to compute a one-year ahead prediction with $\window$ equal to 104 and a $\lag$ equal to 52. For each time series, we fitted 3 per-time-series parametric models: We fit the first one using the 2 first years and compute a forecast of the thrid year.

@@

For the first parametric per-time-series models, we used existing Python or R librarys to estimate the different parameters $\statparam^n$. During the M4 competition, parameters of the exponential smoothing of the porposed hybrid model could move during the training. In our framework,
$\{\statparam^n\}_{1\leqslant n \leqslant N}$ are fixed during the training of the recurrent models. In this section we propose two versions of HERMES depending of the choice of local parametric models. The first one use as predictors an additive exponential smoothing model as a reference close to \cite{smyl2020hybrid}. The second one use as predictors the TBATS model of \cite{doi:10.1198/jasa.2011.tm09771} and  achieves striking accuracy results on our fashion dataset. For the neural network part, we built an architecture summarized in Figure~\ref{fig:rnn_architecture}. It is composed of 3 LSTM layer of shape 50 and a final Dense layer to provide the correct output dimension. We use a classical Adam optimizer with a learning rate equal to 0.005 and a batch size equal to 64. For our loss function, we tested several metrics and we finally converged on the following one :

@@

Against these models, we propose two versions of HERMES called respectively \textit{hermes-ets} and \textit{hermes-tbats} according to the per-time-series model choice.
%Against these models, we propose two versions of our regime switching hybrid recurrent model \textit{rshm}. The first one, that we name \textit{rshm-ets}, is the hybrid model with an additive exponential smoothing model as parametric model. For the second one, we use the TBATS approach as paramteric model and we named it \textit{rshm-tbats}. 
%To reach a higher accuracy level we also propose an ensembling (\textit{ensembling} of our hybrid approach using the FFORMA method created during the M4 competition, see \citep{fforma}).  
Moreover, we evaluate our hybrid framework with the inclusion of our weak signals (ws) referred to as \textit{hermes-ets-ws} and \textit{hermes-tbats-ws}. In order to provide a fair comparison, we also train a \textit{lstm} with the weak signals named \textit{lstm-ws}.

@@

Detecting emerging and declining trends is a crucial issue for the fashion industry. A correct or incorrect prediction could lead to good returns or massive waste due to overstock or unsold clothes. In a given year, we define an increasing trend as a trend that does more than 10\% of growth in terms of Year and Year. In the same way, we define a decreasing trend as a trend that declines by 10\% or more. We classify other trends as flat trends. On the test set, the year 2019, we have 1871 increasing trends, 2016 decreasing trends and 6113 flat trends. In addition to the accuracy metrics, we also compare the different methods on this classification task and especially difference between methode using weak signal or not.

@@

For our 3 metrics and for each model, we compute the average on all our sequences \numberts~  on the final year. Results are displayed in the Table~\ref{tab:metricresults}. For our model using neural networks, we trained 10 models with different seeds and compute the average and the standard deviation for the three metrics. For the statistical models, we can see a large domination of the TBATS model with an OWA equal to 0.850. It is one of the main motivations why we use this model on our best HERMES candidate as the predictor model. However, we can see that the full LSTM model \textit{lstm} is the best model over our benchmark candidates with a OWA equal to 0.825.

Considering our new HERMES approach, we see a large domination of our \textit{hermes-tbats} version with a OWA equal to 0.816 and a strong stability across the different trainings. Regarding \textit{hermes-ets}, we see a huge increase compared to its predictor choice \textit{ets} with a descrease from 0.937 to 0.875 in term of OWA. However, its accuracy remains low in comparison to the \textit{lstm} benchmarck or our HERMES's second version using Tbats. In Figure~\ref{fig:hybrid-examples}, we displayed some examples of \textit{hermes-tbats} model and some weaknessess that it is able to understand and accurately correct.

@@

An interesting constat is that models using our weak signals slightly underperform their relative without-weak-signals models on all our 3 metrics. We see an exception for our \textit{hermes-tabts-ws} that outperform its relative \textit{hermes-tabts} in term of MASE (0.713 compare to 0.715) but it is not clearly significative compare to the standard deviation. The impact of our weak signal is revealed with our classification results.

When we compare our classification results between the \textit{tbats} model and our hybrid method \textit{hermes-tbats} given in Table~\ref{tab:tbatsclass}, we note an impresive diminution of that we called an "unforgiveable error" : forecast an increase instead of a decrease and vice versa. We divide the number of this error by 3 with only a slightly decrease of the number of correct increase/decrease predictions. However, with our weak signals, we see that \textit{hermes-tbats-ws} is able to catch twice as much as its relative model without weak signal while keeping a relatively low number of "unforgivable error".

@@

In addition to our results on our fashion dataset gathering 10000 time series, we also investigate the behaviours of our HERMES model when it is trained on smaller datasets. We did 2 experiences, we train our models on a dataset of 1000 time series and on a dataset of 100 time series. Results are given in Table~\ref{tab:1000metricresults} and Table~\ref{tab:100metricresults}.

With these investigations, we can make two important remarks. First, our hybrid framework \textit{hermes-tbats} achieves the first position in term of global accuracy on both datasets. Due to the strengh of its per-time-series predictor TBATS, our hybrid model succeds at correcting some of its weaknesses and logically reach a striking final accuracy. Secondly, we can note that the accuracy of the full neural network \textit{lstm} decrease according to the dataset size. With a small dataset of 100 time series, a local statistical model like \textit{tbats} or \textit{stlm} can largely outperform its accuracy level. In fact, learn how to compute a full prediction from scratch is a complex task and for a neural network, it evolves a large amout of data. Nevertheless, with our hybrid framework, the RNN task is largely simplify. Our achitectures logicaly needs less data to be train and perform well.

@@

With our results, we can make several interesting conclusions. Firstly, our new HERMES framework is a really promising framework. By mixing the performance of local parametric models and a global DNN, our \textit{hermes-tbats} version clearly outperform traditional statistical methods and full neural network models. Furthermore, this framework is totally suited for dealing with external signals. With a fine pre-processing and a well-designed architecture, our hybrid framework succeed at leveraging our complex extra data and reach impressive accuracy level in term of classification. Secondly, our results bring to light the quality of our new Fashion dataset. We saw that the full LSTM model \textit{lstm} outperforms all time series specific models when it is trained with the biggest dataset of 10000 time series but not with the smaller ones. This shows that complex neural network architectures involve large amount of data to be train and our full dataset is well suited for this. Finally, with the addition of our weak signals, we give a totally new dimension to our new hybrid architecture and our fashion dataset. Our results show that our external weak signals hide a complex but usable predictive power by our HERMES model. However, we believe that it remains a lot of ways to explore in order to leverage the full potential of these chaotic signals.

@@

\bibliography{hermes_paper}
\bibliographystyle{apalike}

@@

%\section{Fashion Dataset overview}
